Mixed Non-Bayesian and DeGroot Learning

### 2012-12-04 docs/paper.tex
Moved report to docs directory
Added some references
Wrote up much of the model.  Working on conversion of DeGroot to Non-Bayesian belief states.

\documentclass[a4paper,12pt]{article}
\usepackage{amsmath} % For 'cases' curly brace
\begin{document}
\title{Mixed Non-Bayesian and DeGroot Learning}
\author{Pedro Barbuda\\pdaquino@umich.edu \and Dan Clark\\ddclark@umich.edu}
\date{December 11, 2012}

@@

@@

We will represent the state of the world as a probability distribution:
\begin{equation}
P^*(x)=\begin{cases}
m^* \cdot x & 0 \le x \le 1 \\
0, & \text{otherwise}
\end{cases}
\end{equation}
The slope $\{ m^* \in \mathbf{R} : -2 \le m^* \le 2 \}$ will be the defining characteristic of the distribution.  We have chosen to bound $m^*$ between -2 and 2 so that the support of $P_t$  is always over $[0,1]$.  The value of the parameter $m^*$ is the ``true'' state that each node is trying to learn.

At each timestep $t$, every Non-Bayesian node $i$ will receive a signal $s_{i,t}$ which is a value drawn from $P_t$.  These observations will be used by the nodes in the network to construct a belief about $m^*$.

@@

To represent a belief about the continuous slope value $m*$ for a Non-Bayesian node we discretize $m$ in the following manner.  Let $\Theta = \{\theta_0, \theta_1,...\theta_n\}, n < \infty$ be the discrete set of possible states of the world over which each Non-Bayesian node holds a distribution of belief. Each $\theta_i$ corresponds to the belief that the slope of $P^*$ is
\begin{equation} \label{eq:theta_meaning}
m^* = \frac{4i}{n - 1} - 2
\end{equation}
As an example, if we take n = 21 belief states, then we have
\begin{equation}
\nonumber
\begin{cases}
& \theta_0: m^* = -2.0 \\
& \theta_1: m^* = -1.9 \\
& ... \\
& \theta_{20}: m^* = 2.0
\end{cases}
\end{equation}
For each Non-Bayesian node $i$, the belief at time $t$ that $\theta_i$ is the true state of the world is denoted by $\mu_{i,t}(\theta_i)$.  Thus $\{ \mu_{i,t}(\theta_1), \mu_{i,t}(\theta_2), ... \mu_{i,t}(\theta_n) \}$ is a probability distribution over the set of world states for fixed $i,t$.

@@

When a DeGroot node a Non-Bayesian neighbor performs an update it must obtain a value 
$m_{j,t}$ for the belief of this node.  This is calculated as

\begin{equation}
m_{j,t} = \sum_{k=1}^n\mu_{j,t}(\theta_k)(\frac{4i}{n - 1} - 2)
\end{equation}

Here we are taking a weighted average of the $m^*$ value represented by each state $\theta_i$ as defined in equation \ref{eq:theta_meaning}, where the weights are given by $j$'s level of belief in each state.

@@

The update of a Non-Bayesian node in our model is handled similarly to the method laid out 
in Jadbabaie et. al. % @todo[DDC] Figure out references system

% [DDC] Just putting in the equations for the moment.

@@

@@

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage{amsmath} % For 'cases' curly brace
\begin{document}
\title{Mixed Non-Bayesian and DeGroot Learning}
\author{Pedro d'Aquino\\pdaquino@umich.edu \and Dan Clark\\ddclark@umich.edu}
\date{December 11, 2012}

@@

\cite{Jadbabaie2012}
\cite{DeGroot1974}

@@

We will represent the state of the world as a probability distribution:
\begin{equation}
p^*(x)=\begin{cases}
m^* \cdot x + \frac{1}{2}(2-m^*) & 0 \le x \le 1 \\
0, & \text{otherwise}
\end{cases}
\end{equation}
The slope $\{ m^* \in \mathbf{R} : -2 \le m^* \le 2 \}$ will be the defining characteristic of the distribution.  We have chosen to bound $m^*$ between -2 and 2 add the term $\frac{1}{2}(2-m^*)$ so that the support of $p^*(x)$  is always over $[0,1]$.  The value of the parameter $m^*$ is the ``true'' state that each node is trying to learn.

At each timestep $t$, every Non-Bayesian node $i$ will receive a signal $s_{i,t}$ which is a value drawn from $p^*(x)$.  These observations will be used by the nodes in the network to construct a belief about $m^*$.

@@

To represent a belief about the continuous slope value $m*$ for a Non-Bayesian node we discretize $m$ in the following manner.  Let $\Theta = \{\theta_0, \theta_1,...\theta_n\}, n < \infty$ be the discrete set of possible states of the world over which each Non-Bayesian node holds a distribution of belief. Each $\theta_i$ corresponds to the belief that the slope of $p^*(x)$ is equal to $m_i$ where
\begin{equation}
\label{eq:theta_meaning}
m_i = \frac{4i}{n - 1} - 2
\end{equation}
As an example, if we take n = 21 belief states, then we have
\begin{equation}
\nonumber
\begin{cases}
& \theta_0: m^* = -2.0 \\
& \theta_1: m^* = -1.9 \\
& ... \\
& \theta_{20}: m^* = 2.0
\end{cases}
\end{equation}
For each Non-Bayesian node $i$, the belief at time $t$ that $\theta_i$ is the true state of the world is denoted by $\mu_{i,t}(\theta_i)$.  Thus $\{ \mu_{i,t}(\theta_1), \mu_{i,t}(\theta_2), ... \mu_{i,t}(\theta_n) \}$ is a probability distribution over the set of world states for fixed $i,t$.

@@

When a DeGroot node with a Non-Bayesian neighbor performs an update it must obtain a value 
$m_{j,t}^\prime$ for the belief of this neighbor.  This is calculated as

\begin{equation}
m_{j,t}^\prime = \sum_{k=1}^n\mu_{j,t}(\theta_k)(\frac{4i}{n - 1} - 2)
\end{equation}

Here we are taking a weighted average of the $m^*$ value represented by each state $\theta_i$ as defined in equation~\ref{eq:theta_meaning}, where the weights are given by $j$'s level of belief in each state.

@@

The update of a Non-Bayesian node in our model is handled similarly to the method laid out 
in \cite{Jadbabaie2012}.  We denote the belief of a node $i$ that it will receive the signal $s_i$ at time $t$ as $m_{i,t}(s_i)$, defined as follows:

@@

% @todo[DDC] More detail for derivation/explanation of likelihood?
In this case the likelihood function $\ell_i(s_i|\theta_i)$ can be obtained from the probability distribution function represented by the belief state $\theta_i$.

\begin{equation}
\label{eq:likelihood}
\ell_i(s_i|\theta_i) = m_i s_i + \frac{1}{2}(2 - m_i)
\end{equation}
where $m_i$ is defined as in equation~\ref{eq:theta_meaning}.

The update of a node's belief in each state $\theta_i$ for a given time period $t$ is then given by

@@

Here the first term is the Bayesian update of the belief $\mu_{i,t}(\theta_i)$ after observing the signal $\omega_{i,t+1}$ multiplied by the node's self reliance $a_{ii}$.  The summation is the linear incorporation of the beilefs of $i$'s neighbors.

This update differs from the previous work in two major ways.  Firstly, we provide each Non-Bayesian node with only a single signal per timestep, where this signal is a single draw from the probability distribution $p^*(x)$.

Secondly, we must define $\mu_{j,t}(\theta_i)$ when $j$ is a DeGroot node.  We consider two methods for doing so, defined in sections \ref{sec:draw_from_degroot} and \ref{sec:likelihood_metric} respectively.

\subsubsection{Belief Distribution from Draw of Probability Distribution}
\label{sec:draw_from_degroot}

The first method that we consider for converting a DeGroot node $j$'s belief to a prior which can be included in a Non-Bayesian node $i$'s belief update involves generating a probability distribution from the $j$'s current belief and drawing from this distribution.  For each DeGroot neighbor of $i$ at time $t$ we define the probability distribution
\begin{equation}
p_{j,t}(x)=\begin{cases}
m_{j,t} x + \frac{1}{2}(2-m^*) & 0 \le x \le 1 \\
0, & \text{otherwise}
\end{cases}
\end{equation}

This is simply the distribution which $j$ believes to be the state of the world.  We then draw a single signal $s_{j,t}^\prime$ from this distribution.  We create a belief distribution $\mu_{j,t}^\prime$ from $s_{j,t}^\prime$ by performing a Bayesian-style update with equal priors.

\begin{equation}
\mu_{j,t}^\prime(\theta_i) = \frac{\ell_i(s_{j,t}^\prime|\theta_i)}{m_{i,t}(s_{j,t}^\prime)}
\end{equation}

This generated belief distribution $\mu_{j,t}^\prime$ is then used as

% @todo[DDC] Still working on this section

\subsubsection{Belief Distribution from Likelihood Distance Metric}
\label{sec:likelihood_metric}

\bibliographystyle{plain}
\bibliography{eecs598Report}
